General constraints on magic distillation protocols from statistical mechanics

### 2021-06-05 magic_paper.tex
added connection between Ha and Da and proof of general bounds

\begin{theorem} Let $\tau$ be in the interior of $\F$, and define $D_\infty(\rho,\tau) := D_\infty(W_\rho(\x) || W_\tau (\x))$. Then $D_\infty(\rho, \tau)$ is well-defined for all $\rho$, and the following hold: \nick{can generalise to $D_{\alpha}$ for appropriate $\alpha$}
\begin{enumerate}
\item $D_\infty(\rho, \tau) \ge 0$ for all quantum states $\rho$.
\item  $D_\infty(\rho , \tau) = 0$ if and only if $\rho =\tau$.
\item $D_\infty(\rho^{\otimes 2n}, \tau^{\otimes 2n}) = n D_\infty(\rho^{\otimes 2} ,\tau^{\otimes 2})$ for any $n \in \mathbb{N}$.
\item For any quantum state $\rho$, and any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$, we have $D_\infty (\rho , \tau) \ge D_\infty (\E(\rho), \E(\tau))$.
\end{enumerate}
\end{theorem}
\begin{proof}
	Since $\tau$ is in the interior of $\F$, its Wigner function obeys $W_\tau(\x) >0$ for all points $\x$ in the phase space. In general, $W_\rho(\x)$ is a quasi-distribution, however since $\sum_{\x} W_\rho (\x) = 1$ this implies it must have at least one positive component, so $\max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)}>0$. Therefore $D_\infty (\rho,\tau)$ is always well-defined.

@@

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.35]{figs/test/H_vs_eps_a.pdf}
    \caption{\ddd{[TO DO: Set $\epsilon = 0$ and determine region of $\alpha$ such that $H <0$.]} Here, the exponent is $\alpha =$ even$/$odd for $1.10 \leq \alpha \leq 1.50$. $H_\alpha$ is increasing in $\alpha$ and $\epsilon$ \nick{should be easy to show analytically}. First dashed contour from the right corresponds to $H_\alpha(\rho_{\rm{S}}(\epsilon)) = 0$. Specifically, $H_\alpha(\rho_{\rm{S}}(0)) = 0$ has a unique solution, which is the \nick{probably irrational - this seems problematic} solution of $3^\alpha - 2^{3-\alpha} = 1$.
    }
    \label{fig:lcs}
\end{figure}

We then prove the following result connecting simple majorization to relative majorization.
\nick{move following lemma to section on relative majorization equivalent conditions}
\begin{lemma}
Let $\w\in \mathbb{R}^N, \w'\in \mathbb{R}^{N'}$ be quasi-distributions and $\r\in \mathbb{R}^N, \r'\in \mathbb{R}^{N'}$ probability distributions with positive rational entries given by $r_i = a_i/K$ and $r_i' = a_i'/K$ for positive integers $a_i, a_i'$ and $K = \sum_{i=1}^N a_i = \sum_{i=1}^{N'} a_i'$. 
Then,
\begin{equation}
(\w, \r) \succ (\w', \r') \mbox{ if and only if } \Gamma_{\bma} (\w) \succ \Gamma_{\bma'} (\w'),
\end{equation}
where the embedding map $\Gamma_{\bma} :\mathbb{R}^N \rightarrow \mathbb{R}^K$ is given by
\begin{equation}
	\Gamma_{\bma}(\x) := \bigoplus_{i=1}^N x_i \eta_{a_i},
\end{equation}
with $\eta_{a_i} = (1/a_i, 1/a_i, \dots, 1/a_i)$ the uniform distribution on $a_i$ elements.
\end{lemma}
\begin{proof}
	We first note that the map $\Gamma_{\bma}$ is stochastic and has a well-defined left-inverse $\Gamma^{-1}_{\bma'}: \mathbb{R}^K \rightarrow \mathbb{R}^N$ given by
\begin{equation}
	\Gamma^{-1}_{\bma}(\w) = \left( \sum_{i=1}^{a_1} w_i,  \sum_{i = a_1 +1}^{a_1 + a_2} \hspace{-5pt} w_i, \dots , \hspace{-15pt} \sum_{i=a_1 + \dots + a_{N-1}+1}^{K} \hspace{-10pt} w_i \right),
\end{equation}
that obeys $(\Gamma^{-1}_{\bma} \circ \Gamma_{\bma}) (\x) = \x$ for all $\x \in \mathbb{R}^N$.

@@

\subsubsection{Unital fragment}

@@

\ddd{[TO-DO TIDY AND CHECK]}
\begin{theorem}\label{thm:HSchur}
	Let $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$.
	Then, $H_\alpha$ is Schur-concave, i.e. for quasi-distributions $\w, \w' \in \mathbb{R}^N$, we have $H_\alpha(\w) \leq H_\alpha(\w')$, whenever $\w \succ \w'$.
\end{theorem}
\begin{proof}
We have $\alpha = \frac{2a}{2b+1} \geq \frac{2b}{2b-1} > 1$ and $\alpha$ is a rational with even numerator and odd denominator, so $\sum_i x_i^\alpha > 0$ and $H_\alpha(\x)$ is well-defined for all quasi-distributions $\x$.

@@

Therefore, whenever $w_i \geq w_j$, we have that 
\begin{equation}
	-w_i^{\alpha-1} \leq -w_j^{\alpha-1},
\end{equation}
which leads to
\begin{equation}
	\frac{\partial H_\alpha}{\partial w_i} \leq \frac{\partial H_\alpha}{\partial w_j}.
\end{equation}
Therefore, $H_\alpha$ is Schur-concave and
\begin{equation}
	H_\alpha(\w) \leq H_\alpha(\w'),
\end{equation}
for any quasi-distributions $\w, \w'$ that obey $\w \succ \w'$.

\begin{table}[h]
  \def\arraystretch{1.5}
  \centering
  \begin{tabular}{c|c|c|c||c|c}
    $w_i$ & $w_{i+1}$ & $\alpha$ & $\frac{w_i^{\alpha-1}}{\alpha-1} \geq \frac{w_{i+1}^{\alpha-1}}{\alpha-1}$ & $\alpha$ & $\frac{w_i^{\alpha-1}}{\alpha-1} \geq \frac{w_{i+1}^{\alpha-1}}{\alpha-1}$ \\[0.5ex]\hline
    $2$ & $1.5$  & $3$ & $2 > 1.125$ T & $1/3$ & $-0.94 > -1.14$ T \\
    $2$ & $-1.5$ & $3$ & $2 > 1.125$ T & $1/3$ & $-0.94 > -1.14$ T \\
    $2$ & $-2.5$ & $3$ & $2 < 3.125$ F & $1/3$ & $-0.94 < -0.81$ F \\[0.5ex]\hline
    $2/3$ & $1/3$  & $3$ & $0.22 > 0.06$ T & $1/3$ & $-1.97 > -3.12$ T \\
    $2/3$ & $-1/3$ & $3$ & $0.22 > 0.06$ T & $1/3$ & $-1.97 > -3.12$ T \\
    $2/3$ & $-4/3$ & $3$ & $0.22 < 0.89$ F & $1/3$ & $-1.97 < -1.24$ F \\[0.5ex]\hline
    $2$ & $1.5$  & $4$ & $2.67 > 1.125$ T & $2/3$ & $-2.38 > -2.62$ T \\
    $2$ & $-1.5$ & $4$ & $2.66 > -1.125$ T & $2/3$ & $-2.38 > 2.62$ F \\
    $2$ & $-2.5$ & $4$ & $2.66 > 5.21$ T & $2/3$ & $-2.38 > 2.21$ F \\
    $-2$ & $-2.5$ & $4$ & $-2.66 > -5.21$ T & $2/3$ & $2.38 > 2.21$ T \\[0.5ex]\hline
    $2/3$ & $1/3$  & $4$ & $0.10 > 0.01$ T & $2/3$ & $-3.43 > -4.33$ T \\
    $2/3$ & $-1/3$ & $4$ & $0.10 > -0.01$ T & $2/3$ & $-3.43 > 4.33$ F \\
    $2/3$ & $-4/3$ & $4$ & $0.10 > -0.79$ T & $2/3$ & $-3.43 > 2.73$ F \\
    $-1/3$ & $-2/3$ & $4$ & $-0.01 > -0.10$ T & $2/3$ & $4.33 > 3.43$ T \\
    $-1/3$ & $-4/3$ & $4$ & $-0.01 > -0.79$ T & $2/3$ & $4.33 > 2.73$ T
  \end{tabular}
  \caption{\nick{NUMERICS ON SCHUR-OSTROWSKI CONDITION} The case $\alpha=$ even$/$odd and $\alpha > 1$ works for any combination of $w_i, w_{i+1}$ with $w_i > w_{i+1}$. 
  All other cases do not work.}
  \label{tab:test}
\end{table}

\end{proof}
The set $F := \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the rationals $\mathbb{Q}_{>1}$, which in turn are dense in the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by a sequence $f_n := c2^n / (d2^n+1)$ with every element $f_n$ in the set $F$. \nick{can turn into lemma}

We can now derive the following entropic bounds on magic state transformations.
\begin{theorem}
	Consider a general magic state distillation process $\rho^{\otimes n} \rightarrow \rho'^{\otimes n'}$	in the unital fragment.
	We have the following family of upper bounds on the distillation rate $R := n'/n$,
	\begin{equation}
		R \leq \frac{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho \right)}{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho') \right)} = \frac{D_{\alpha}(\rho||\id/3)}{D_{\alpha}(\rho'||\id/3)},
	\end{equation}
	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$.
\end{theorem}
\begin{proof}
	For the given form of $\alpha$, $H_\alpha(\sigma)$ is well-defined adn Schur-concave for all quantum states $\sigma$.

	We first regularise the number of output copies in the state distillation by tensoring in $(n-n')$ copies of the (free) maximally mixed state $\id/3$, so that we instead consider the process
\begin{equation}
	\rho^{\otimes n} \rightarrow \rho'^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n - n')}.
\end{equation}
Since we have that $W_{\rho^{\otimes n}}(\bmx) \succ_{\id/3} W_{\rho'^{\otimes n'}}(\bmx)$, by Schur-concativity of $H_\alpha$ we obtain
\begin{equation}
	H_\alpha \left( \rho^{\otimes n} \right) \leq H_\alpha \left( \rho'^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n - n')} \right).
\end{equation}
By additivity of $H_\alpha$, we can rewrite the inequality as
\begin{equation}
	n H_\alpha \left( \rho \right) \leq n' H_\alpha \left( \rho' \right) + (n - n') H_\alpha \left( \id/3 \right).
\end{equation}
Now, $H_\alpha \left( \id/3 \right)$ is the maximum value of $H_\alpha(\rho)$ for unital processes because every state $\rho$ majorizes $\id/3$, so we can finally re-arrange the inequality to
\begin{equation}
	\frac{n'}{n} \leq \frac{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho \right)}{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho' \right)}.
\end{equation}
\end{proof}

\subsubsection{Extention to general relative majorization}

Therefore if we have a Schur-Concave function $f(\x)$ for majorization of quasi-distributions then we can define a monotonic function for relative majorization via composition with $\Gamma_{\mathbf{a}}$ and its inverse.
This should provide relative majorization monotones from which we can obtain distillation bounds, such as
\begin{equation}
R \le \frac{F_\alpha(\tau) - F_\alpha (\rho)}{F_\alpha(\tau') - F_\alpha (\rho')}.
\end{equation}
\ddd{[To be checked...transition from entropies to free energies less obvious from this route...needs reflection]}

This is probably all we need to show:
\begin{equation}
H_\alpha(\Gamma_{\mathbf{a}}(\p)) = D_\alpha(\p ||\r),
\end{equation}
where we define the Renyi relative entropy
\begin{equation}
D_\alpha (\p || \r) := \frac{1}{\alpha -1} \log \sum_i p_i^\alpha q_i^{1-\alpha}.
\end{equation}
This probably follows from the details of how the $\Gamma_{\mathbf{a}}$ relates to $\r$. Needs expanding carefully.

\begin{theorem}
	Consider a general magic state distillation process that converts magic state $\rho^{\otimes n} \longrightarrow \rho'^{\otimes n'}$ as well as equilibrium state $\tau^{\otimes n} \longrightarrow \tau'^{\otimes n'}$, where we assume that $W_{\tau^{\otimes n}}(\bmx) = a_{\bmx}/K$ and $W_{\tau'^{\otimes n'}}(\bmx) = a_{\bmx}/K$ for positive integers $a_{\bmx}, a_{\bmx}'$ and $K = \sum_{\bmx} a_{\bmx} = \sum_{\bmx} a_{\bmx}'$.  \nick{It may be more convenient to consider $W_{\tau}(\bmx') = a_{\bmx'}/K$, so that $K$ ends up raised to the power of $n$}

	We have the following family of upper bounds on the distillation rate $R := n'/n$,
	\begin{equation}
		R \leq \text{\nick{BOUND}},
	\end{equation}
	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$.
\end{theorem}
\begin{proof}
	For the sake of clarity, we write $\rho_n \coloneqq \rho_S(\epsilon)^{\otimes n}$, $\rho'_{n'} \coloneqq \rho_S(\epsilon')^{\otimes n'}$, $\tau_n \coloneqq \tau^{\otimes n}$ and $\tau'_{n'} \coloneqq \tau'^{\otimes n'}$.

	We have that 
\begin{equation}	
	\Big(W_{\rho_n}(\bmx), W_{\tau_n}(\bmx')\Big) \succ \Big(W_{\rho'_{n'}}(\bmx), W_{\tau'_{n'}}(\bmx')\Big)
\end{equation}	
or equivalently $\Gamma_{\bma}(W_{\rho_n}(\bmx)) \succ \Gamma_{\bma'}(W_{\rho'_{n'}}(\bmx))$ for all $\bmx$, where
\begin{align}
	\Gamma_{\bma}(W_{\rho_n}) &= \bigoplus_{\bmx} W_{\rho_n}(\bmx) \left(\frac{1}{KW_{\tau_n}(\bmx)}, \dots, \frac{1}{KW_{\tau_n}(\bmx)} \right)\nonumber\\
	&= \frac{1}{K}\bigoplus_{\bmx} \Big( W_{\rho_n|\tau_n}(\bmx), \dots, W_{\rho_n|\tau_n}(\bmx) \Big)
\end{align}
and similarly for $\Gamma_{\bma'}(W_{\rho'_{n'}})$.
Therefore,
\begin{align}
	&H_{\alpha}(\Gamma_{\bma}(W_{\rho_n})) = \frac{1}{1-\alpha} \log_2 \left( \frac{d^{2n}}{K^\alpha} \sum_{\bmx} \big[ W_{\rho_n|\tau_n}(\bmx) \big]^\alpha \right) = \nonumber\\
	&\frac{1}{1-\alpha} \log_2 \left( \frac{d^{2n}}{K^\alpha} \sum_{\bmx_1, \dots, \bmx_n} \big[ W_{\rho|\tau}(\bmx_1) \dots W_{\rho|\tau}(\bmx_n) \big]^\alpha \right)
\end{align}
while
\begin{equation}
	D(\rho||\tau) = \frac{1}{\alpha-1} \log_2 \sum_{\bmx} \frac{W_{\rho}(\bmx)^\alpha}{W_{\tau}(\bmx)^{\alpha-1}}.
\end{equation}
\nick{correct mistakes, bridge gaps}
\end{proof}

>>>>

\begin{theorem} Let $\tau$ be in the interior of $\F$, and define $D_\infty(\rho,\tau) := D_\infty(W_\rho(\x) || W_\tau (\x))$. Then $D_\infty(\rho, \tau)$ is well-defined for all $\rho$, and the following hold:
\begin{enumerate}
\item $D_\infty(\rho, \tau) \ge 0$ for all quantum states $\rho$.
\item  $D_\infty(\rho , \tau) = 0$ if and only if $\rho =\tau$.
\item $D_\infty(\rho^{\otimes 2n}, \tau^{\otimes 2n}) = n D_\infty(\rho^{\otimes 2} ,\tau^{\otimes 2})$ for any $n \in \mathbb{N}$. \nick{annoying that it doesn't agree with the simpler property of $D_\alpha$ for finite $\alpha$ in~\cref{thm:Da_props}}
\item For any quantum state $\rho$, and any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$, we have $D_\infty (\rho , \tau) \ge D_\infty (\E(\rho), \E(\tau))$.
\end{enumerate}
\end{theorem}
\begin{proof}
	Since $\tau$ is in the interior of $\F$, its Wigner function obeys $W_\tau(\x) >0$ for all points $\x$ in the phase space. In general, $W_\rho(\x)$ is a quasi-distribution, however since $\sum_{\x} W_\rho (\x) = 1$ this implies it must have at least one positive component, so $\max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)}>0$. Therefore $D_\infty (\rho,\tau)$ is always well-defined.

@@

\begin{table}[h]
  \def\arraystretch{1.5}
  \centering
  \begin{tabular}{c|c|c|c||c|c}
    $w_i$ & $w_{i+1}$ & $\alpha$ & $\frac{w_i^{\alpha-1}}{\alpha-1} \geq \frac{w_{i+1}^{\alpha-1}}{\alpha-1}$ & $\alpha$ & $\frac{w_i^{\alpha-1}}{\alpha-1} \geq \frac{w_{i+1}^{\alpha-1}}{\alpha-1}$ \\[0.5ex]\hline
    $2$ & $1.5$  & $3$ & $2 > 1.125$ T & $1/3$ & $-0.94 > -1.14$ T \\
    $2$ & $-1.5$ & $3$ & $2 > 1.125$ T & $1/3$ & $-0.94 > -1.14$ T \\
    $2$ & $-2.5$ & $3$ & $2 < 3.125$ F & $1/3$ & $-0.94 < -0.81$ F \\[0.5ex]\hline
    $2/3$ & $1/3$  & $3$ & $0.22 > 0.06$ T & $1/3$ & $-1.97 > -3.12$ T \\
    $2/3$ & $-1/3$ & $3$ & $0.22 > 0.06$ T & $1/3$ & $-1.97 > -3.12$ T \\
    $2/3$ & $-4/3$ & $3$ & $0.22 < 0.89$ F & $1/3$ & $-1.97 < -1.24$ F \\[0.5ex]\hline
    $2$ & $1.5$  & $4$ & $2.67 > 1.125$ T & $2/3$ & $-2.38 > -2.62$ T \\
    $2$ & $-1.5$ & $4$ & $2.66 > -1.125$ T & $2/3$ & $-2.38 > 2.62$ F \\
    $2$ & $-2.5$ & $4$ & $2.66 > 5.21$ T & $2/3$ & $-2.38 > 2.21$ F \\
    $-2$ & $-2.5$ & $4$ & $-2.66 > -5.21$ T & $2/3$ & $2.38 > 2.21$ T \\[0.5ex]\hline
    $2/3$ & $1/3$  & $4$ & $0.10 > 0.01$ T & $2/3$ & $-3.43 > -4.33$ T \\
    $2/3$ & $-1/3$ & $4$ & $0.10 > -0.01$ T & $2/3$ & $-3.43 > 4.33$ F \\
    $2/3$ & $-4/3$ & $4$ & $0.10 > -0.79$ T & $2/3$ & $-3.43 > 2.73$ F \\
    $-1/3$ & $-2/3$ & $4$ & $-0.01 > -0.10$ T & $2/3$ & $4.33 > 3.43$ T \\
    $-1/3$ & $-4/3$ & $4$ & $-0.01 > -0.79$ T & $2/3$ & $4.33 > 2.73$ T
  \end{tabular}
  \caption{\nick{NUMERICS ON SCHUR-OSTROWSKI CONDITION} The case $\alpha=$ even$/$odd and $\alpha > 1$ works for any combination of $w_i, w_{i+1}$ with $w_i > w_{i+1}$. 
  All other cases do not work.
  I put it here cause it's clunky}
  \label{tab:test}
\end{table}

@@

We prove the following result connecting simple majorization to relative majorization.
\nick{move following lemma to section on relative majorization equivalent conditions}
\begin{lemma}
Let $\w\in \mathbb{R}^N, \w'\in \mathbb{R}^{N'}$ be quasi-distributions and $\r\in \mathbb{R}^N, \r'\in \mathbb{R}^{N'}$ probability distributions with positive rational entries given by $r_i = a_i/K$ and $r_i' = a_i'/K$ for positive integers $a_i, a_i'$ and $K = \sum_{i=1}^N a_i = \sum_{i=1}^{N'} a_i'$. 
Then,
\begin{equation}
(\w, \r) \succ (\w', \r') \mbox{ if and only if } \Gamma_{\bma} (\w) \succ \Gamma_{\bma'} (\w'),
\end{equation}
where the embedding map $\Gamma_{\bma} :\mathbb{R}^N \rightarrow \mathbb{R}^K$ is given by
\begin{equation}
	\Gamma_{\bma}(\x) := \bigoplus_{i=1}^N x_i \eta_{a_i},
\end{equation}
with $\eta_{a_i} = (1/a_i, 1/a_i, \dots, 1/a_i)$ the uniform distribution on $a_i$ elements.
\end{lemma}
\begin{proof}
	We first note that the map $\Gamma_{\bma}$ is stochastic and has a well-defined left-inverse $\Gamma^{-1}_{\bma'}: \mathbb{R}^K \rightarrow \mathbb{R}^N$ given by
\begin{equation}
	\Gamma^{-1}_{\bma}(\w) = \left( \sum_{i=1}^{a_1} w_i,  \sum_{i = a_1 +1}^{a_1 + a_2} \hspace{-5pt} w_i, \dots , \hspace{-15pt} \sum_{i=a_1 + \dots + a_{N-1}+1}^{K} \hspace{-10pt} w_i \right),
\end{equation}
that obeys $(\Gamma^{-1}_{\bma} \circ \Gamma_{\bma}) (\x) = \x$ for all $\x \in \mathbb{R}^N$.

@@

\subsubsection{Classical $\alpha$-Renyi entropy and divergence for quasi-distributions}

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.35]{figs/test/H_vs_eps_a.pdf}
    \caption{\ddd{[TO DO: Set $\epsilon = 0$ and determine region of $\alpha$ such that $H <0$.]} Here, the exponent is $\alpha =$ even$/$odd for $1.10 \leq \alpha \leq 1.50$. $H_\alpha$ is increasing in $\alpha$ and $\epsilon$ \nick{should be easy to show analytically}. First dashed contour from the right corresponds to $H_\alpha(\rho_{\rm{S}}(\epsilon)) = 0$. Specifically, $H_\alpha(\rho_{\rm{S}}(0)) = 0$ has a unique solution, which is the \nick{probably irrational} solution of $3^\alpha - 2^{3-\alpha} = 1$.
    }
    \label{fig:lcs}
\end{figure}

@@

\begin{theorem}\label{thm:HSchur}
	Let $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$.
	Then, $H_\alpha$ is Schur-concave, i.e. for quasi-distributions $\w, \w' \in \mathbb{R}^N$, we have $H_\alpha(\w) \leq H_\alpha(\w')$, whenever $\w \succ \w'$.
\end{theorem}
\begin{proof}
We have $\alpha = \frac{2a}{2b+1} \geq \frac{2b}{2b-1} > 1$ and $\alpha$ is a rational with even numerator and odd denominator, so $\sum_i x_i^\alpha > 0$ and $H_\alpha(\x)$ is well-defined for all quasi-distributions $\x$.

@@

Therefore, whenever $w_i \geq w_j$, we have that 
\begin{equation}
	-w_i^{\alpha-1} \leq -w_j^{\alpha-1},
\end{equation}
which leads to
\begin{equation}
	\frac{\partial H_\alpha}{\partial w_i} \leq \frac{\partial H_\alpha}{\partial w_j}.
\end{equation}
Therefore, $H_\alpha$ is Schur-concave and
\begin{equation}
	H_\alpha(\w) \leq H_\alpha(\w'),
\end{equation}
for any quasi-distributions $\w, \w'$ that obey $\w \succ \w'$.
\end{proof}
The set $F := \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the rationals $\mathbb{Q}_{>1}$, which in turn are dense in the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by a sequence $f_n := c2^n / (d2^n+1)$ with every element $f_n$ in the set $F$. \nick{can turn into lemma}

Now we define the classical $\alpha$-Renyi divergence in terms of the Wigner quasi-distribution of any magic state $\rho$ and the Wigner probability distribution of any equilibrium state $\tau$ as
\begin{equation}
	D_\alpha(\rho || \tau) := \frac{1}{\alpha - 1} \log_2 \sum_{\bmx} W_{\rho}(\bmx)^\alpha W_{\tau}(\bmx)^{1-\alpha},
\end{equation}
where $\alpha$ can take values of the form $2a / (2b+1)$, for non-negative integers $a,b$ to ensure that the argument of the logarithm is positive.
\nick{Notation clashes with quantum Renyi divergence}

We can connect the $\alpha$-Renyi entropy and divergence for quasi-distributions via the following result.

\begin{theorem}\label{thm:H2D}
	Let $\w\in \mathbb{R}^N$ be a quasi-distribution and $\r \in \mathbb{R}^N$ a probability distribution with positive rational entries given by $r_i = a_i/K$ for positive integers $a_i$ and $K = \sum_{i=1}^N a_i$.
	Then,
	\begin{equation}
		H_\alpha(\Gamma_{\bma}(\w)) = K - D_\alpha(\w ||\r),
	\end{equation}
	where $\alpha = 2c / (2d+1)$ for non-negative integers $c,d$ such that $H_\alpha(\x)$ is well-defined for all $\x$.
\end{theorem}
\begin{proof}
	For the given form of $\alpha$ and positive $r_i,\ i=1,\dots,N$, $D_\alpha(\x ||\r)$ is well-defined for all $\x$.

	The expression follows from the definition of $\Gamma_{\bma}$ which gives
	\begin{equation}
		\Gamma_{\bma}(\w) = \bigoplus_{i=1}^N w_i (1/a_i, 1/a_i, \dots, 1/a_i).
	\end{equation}
	This directly leads to
	\begin{align}
		H_\alpha(\Gamma_{\bma}(\w)) &= \frac{1}{1-\alpha} \log_2 \sum_{i=1}^N a_i \left( \frac{w_i}{a_i} \right)^\alpha \nonumber\\
		&= \frac{1}{1-\alpha} \log_2 \sum_{i=1}^N w_i^{\alpha} a_i^{1-\alpha} \nonumber\\
		&= \frac{1}{1-\alpha} \log_2 K^{1-\alpha} \sum_{i=1}^N w_i^{\alpha} \nonumber\\
		&= K + \frac{1}{1-\alpha} \log_2 \sum_{i=1}^N w_i^{\alpha} r_i^{1-\alpha} \nonumber\\
		&= K - D_\alpha(\w ||\r).
	\end{align}
\end{proof}

\begin{theorem}\label{thm:Da_props} 
	Let $\tau$ be a state in the interior of $\F$ and $\alpha = 2a / (2b+1)$ for non-negative integers $a,b$
Then, the $\alpha$-Renyi divergence $D_\alpha(\rho, \tau)$ is well-defined for all states $\rho$, and the following hold:
\begin{enumerate}
\item $D_\alpha(\rho || \tau) \ge 0$ for all quantum states $\rho$.
\item  $D_\alpha(\rho || \tau) = 0$ if and only if $\rho =\tau$.
\item $D_\alpha(\rho^{\otimes n} || \tau^{\otimes n}) = n D_\alpha(\rho, \tau)$ for any $n \in \mathbb{N}$.
\item $D_\alpha(\rho || \tau) \geq D_\alpha (\E(\rho) || \E(\tau))$ for any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$.
\end{enumerate}
\end{theorem}
\begin{proof}
	Since $\tau$ is in the interior of $\F$, its Wigner function obeys $W_\tau(\x) >0$ for all points $\x$ in the phase space. 
In general, $W_\rho(\x)$ is a quasi-distribution, but the given form of $\alpha$ ensures that $W_{\rho}(\bmx)^\alpha \geq 0$. 
Therefore $D_\alpha (\rho || \tau)$ is always well-defined.

1. \nick{looks true numerically, maybe can use~\cref{thm:H2D}}

2. Assume $D_\alpha (\rho,\tau) = 0$.
Then,
\begin{equation}
	\sum_{\bmx} W_{\tau}(\bmx) \left( \frac{W_\rho(\x)}{W_\tau(\x)} \right)^\alpha = 1,
\end{equation}
\nick{so...}.
The converse holds by inspection.

3. This property follows from the multiplicativity of the WIgner distribution.
In particular,
\begin{align}
	&D_\alpha(\rho^{\otimes n} || \tau^{\otimes n}) &= \frac{1}{\alpha - 1} \log_2 \sum_{\bmx} W_{\rho^{\otimes n}}(\bmx)^\alpha W_{\tau^{\otimes n}}(\bmx)^{1-\alpha} = \nonumber\\
	&= n D_{\alpha}(\rho || \tau). \nick{complete steps}
\end{align}

4. \nick{This must hold due to~\cref{thm:H2D}}
\end{proof}

\subsubsection{General entropic bounds}

We first derive the following entropic bounds on magic state transformations for unital processes.
\begin{theorem}
	Consider a general magic state distillation process $\rho^{\otimes n} \rightarrow \rho'^{\otimes n'}$	in the unital fragment.
	We have the following family of upper bounds on the distillation rate $R := n'/n$,
	\begin{equation}
		R \leq \frac{D_{\alpha}(\rho||\id/3)}{D_{\alpha}(\rho'||\id/3)},
	\end{equation}
	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$.
\end{theorem}
\begin{proof}
	For the given form of $\alpha$, $H_\alpha(\sigma)$ is well-defined adn Schur-concave for all quantum states $\sigma$.

	We first regularise the number of output copies in the state distillation by tensoring in $(n-n')$ copies of the (free) maximally mixed state $\id/3$, so that we instead consider the process
\begin{equation}
	\rho^{\otimes n} \rightarrow \rho'^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n - n')}.
\end{equation}
Since we have that $W_{\rho^{\otimes n}}(\bmx) \succ_{\id/3} W_{\rho'^{\otimes n'}}(\bmx)$, by Schur-concativity of $H_\alpha$ we obtain
\begin{equation}
	H_\alpha \left( \rho^{\otimes n} \right) \leq H_\alpha \left( \rho'^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n - n')} \right).
\end{equation}
By additivity of $H_\alpha$, we can rewrite the inequality as
\begin{equation}
	n H_\alpha \left( \rho \right) \leq n' H_\alpha \left( \rho' \right) + (n - n') H_\alpha \left( \id/3 \right).
\end{equation}
Now, $H_\alpha \left( \id/3 \right)$ is the maximum value of $H_\alpha(\rho)$ for unital processes because every state $\rho$ majorizes $\id/3$, so we can finally re-arrange the inequality to
\begin{equation}
	\frac{n'}{n} \leq \frac{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho \right)}{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho' \right)} = \frac{D_{\alpha}(\rho||\id/3)}{D_{\alpha}(\rho'||\id/3)}.
\end{equation}
\end{proof}

\ddd{Therefore if we have a Schur-Concave function $f(\x)$ for majorization of quasi-distributions then we can define a monotonic function for relative majorization via composition with $\Gamma_{\mathbf{a}}$ and its inverse.
This should provide relative majorization monotones from which we can obtain distillation bounds, such as
\begin{equation}
	R \le \frac{F_\alpha(\tau) - F_\alpha (\rho)}{F_\alpha(\tau') - F_\alpha (\rho')}.
\end{equation}}
\nick{I don't understand where the free energies came from. Are they known to be Schur-concave?}

\begin{theorem}
	Consider a general magic state distillation process that converts a magic state $\rho^{\otimes n} \longrightarrow \rho'^{\otimes n'}$ as well as an equilibrium state $\tau^{\otimes n} \longrightarrow \tau'^{\otimes n'}$

	We have the following family of upper bounds on the distillation rate $R := n'/n$,
	\begin{equation}
		R \leq \frac{D_{\alpha}(\rho||\tau)}{D_{\alpha}(\rho'||\tau')},
	\end{equation}
	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$.
\end{theorem}
\begin{proof}
	For the sake of clarity, we write $\rho_n \coloneqq \rho_S(\epsilon)^{\otimes n}$, $\rho'_{n'} \coloneqq \rho_S(\epsilon')^{\otimes n'}$, $\tau_n \coloneqq \tau^{\otimes n}$ and $\tau'_{n'} \coloneqq \tau'^{\otimes n'}$.

	We have that 
\begin{equation}	
	\Big(W_{\rho_n}(\bmx), W_{\tau_n}(\bmx')\Big) \succ \Big(W_{\rho'_{n'}}(\bmx), W_{\tau'_{n'}}(\bmx')\Big)
\end{equation}	
or equivalently $\Gamma_{\bma}(W_{\rho_n}(\bmx)) \succ \Gamma_{\bma'}(W_{\rho'_{n'}}(\bmx))$ for all $\bmx$.

For the given form of $\alpha$, $H_{\alpha}$ is Schur-concave due to~\cref{thm:HSchur}, so
\begin{equation}
	H_{\alpha}(\Gamma_{\bma}(W_{\rho_n})) \leq H_{\alpha}(\Gamma_{\bma'}(W_{\rho'_{n'}})),
\end{equation}
and we can use~\cref{thm:H2D} to rewrite the inequality as
\begin{equation}
	K - D_{\alpha}(W_{\rho_n} || W_{\tau_n}) \leq K - D_{\alpha}(W_{\rho'_{n'}} || W_{\tau'_{n'}}),
\end{equation}.
Due to~\cref{thm:Da_props}, we can rewrite the inequality as
\begin{equation}
	K - nD_{\alpha}(W_{\rho} || W_{\tau_n}) \leq K - n'D_{\alpha}(W_{\rho'} || W_{\tau'_{n'}}),
\end{equation}
and then it is clear that we can rearrange it to
\begin{equation}
	\frac{n'}{n} \leq \frac{D_{\alpha}(\rho||\tau)}{D_{\alpha}(\rho'||\tau')}.
\end{equation}
\end{proof}
